Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-08 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex
Deleted "indirect" correlation part

\subsection{\emph{Indirect} combination of SICM and FM}

% Abschnitt weitere Korrelationen (indirekte)

Beside \emph{direct} combinations in one instrument and correlations, which are displaying images 
obtained by SICM and fluorescence microscopy of the same cell/same region, also \emph{indirect} 
correlations exist. They are showing images under comparable conditions and extent the 
investigation to aspects, which could not be obtained by using one technique alone. Such 
\emph{indirect} correlations were used for investigating the uptake of nanotubes \cite{Lee2013}, 
nanoparticles \cite{Gesper2017} or for investigating healthy and failing myocytes \cite{Lyon2009}. 
Nevertheless is it important to mention, that they could just giving hints of correlations, it 
is not directly comparable with investigations of both in the same cell.

>>>>

% \subsection{\emph{Indirect} combination of SICM and FM}

% Beside \emph{direct} combinations in one instrument and correlations, which are displaying 
% images obtained by SICM and fluorescence microscopy of the same cell/same region, also 
% \emph{indirect} correlations exist. They are showing images under comparable conditions and 
% extent the investigation to aspects, which could not be obtained by using one technique alone. 
% Such \emph{indirect} correlations were used for investigating the uptake of nanotubes 
% \cite{Lee2013}, nanoparticles \cite{Gesper2017} or for investigating healthy and failing 
% myocytes \cite{Lyon2009}. Nevertheless is it important to mention, that they could just giving 
% hints of correlations, it is not directly comparable with investigations of both in the same 
% cell.
